\documentclass{article}

\usepackage[margin=0.5in]{geometry}

\begin{document}

\section*{Fertilizer}
\begin{itemize}
	\itemsep0em
	\item About 10 gallons Complete Organic Fertilizer (COF).
	\begin{itemize}
		\itemsep0em
		\item 4 parts Seed Meal (Cottonseed/Canola).
		\item $\frac{1}{2}$ part Lime.
		\item $\frac{1}{2}$ part Phosphate Rock or Bone-Meal (steamed or raw).
		\item $\frac{1}{2}$ part Kelp Meal (or any kind of pure seaweed meal).
		\item 1 large, vermin-proof container.
	\end{itemize}
	\item Blood Meal.
\end{itemize}

\section*{Seeds}
\begin{itemize}
	\itemsep-.05in
	\item At least 20 vermin-proof seed containers.
	\item 36 Potato seeds.
	\item 450 Spinach seeds.
	\item 264 Beet seeds.
	\item 24 Winter Squash seeds.
	\item 60 Cucumber seeds.
	\item 18 Summer Squash seeds.
	\item 45 Italian Broccoli seeds.
	\item 830 Lettuce seeds.
	\item 392 Carrot seeds.
	\item 54 Tomato seeds.
	\item 768 Long-day Onion seeds.
	\item 576 Pea seeds.
	\item 36 Pole Bean seeds.
	\item 1088 Short-day Onion seeds.
	\item 20 Kale seeds.
	\item 48 Garlic seeds.
\end{itemize}

\section*{Equipment}
\begin{itemize}
	\itemsep0em
	\item Hoe.
	\item Cloche (for tomatoes).
	\begin{itemize}
		\itemsep0em
		\item $\frac{1}{2}$-inch thick galvanized thinwall conduit or plastic pipe, 7-8 feet long.
		\item 30-feet long, 10-foot wide clear poly sheeting.
		\item 60 feet total of 4-by-4 anchors.
	\end{itemize}
	\item Trelise (for tomatoes).
	\begin{itemize}
		\itemsep0em
		\item 6 $8$-in 2-by-4s.
		\item Nails?
		\item Twine.
	\end{itemize}
	\item Fence.
	\begin{itemize}
		\itemsep0em
		\item 4-6 Wooden posts $10 \frac{1}{2}$ in. tall, $5$ in. diameter.
		\item 14 10-ft Studded-``T'' line posts.
		\item At least 228 ft. length of woven wire up to at least $58$ in. tall.
		\item At least 228 ft. length of other obstruction no more than 5 in. apart \& at least 18 in. tall.
		\begin{itemize}
			\item $14 \frac{1}{2}$ gauge filler wire.
			\item 11 gauge top \& bottom wires.
			\item Vertical stays no more than $6$ in. apart.
		\end{itemize}
		\item At least 200 $1 \frac{1}{2}$ staples.
		\item Non-copper-type wood preservative (unless using yew wood).
	\end{itemize}
\end{itemize}

\end{document}
