\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{longtable}

\begin{document}

\begin{longtable}{r|r|l}
	Initial & Date & Task \\ \hline
	\multicolumn{3}{c}{\textbf{March}} \\ \hline
	& 1 & Prepare pea patch. \\ \hline
	& 1 & Sow peas. \\ \hline
	& 1 & Prepare spinach patch. \\ \hline
	& 1 & Sow spinach. \\ \hline
	& 1 & Start onions. \\ \hline
	& 1 & Prepare beet patch. \\ \hline
	& 1 & Prepare broccoli patch. \\ \hline
	& 1 & Prepare carrot patch. \\ \hline
	& 1 & Prepare lettuce patch. \\ \hline
	& 1 & Prepare potato patch. \\ \hline
	& 1 & Prepare squash patch. \\ \hline
	& 1 & Prepare cucumber patch. \\ \hline
	& 1 & Build fence. \\ \hline
	& 16 & Sow peas. \\ \hline
	& 21 & Side-dress spinach (after germination). \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{April}} \\ \hline
	& 1 & Move onion transplants outdoors. \\ \hline
	& 1 & Sow broccoli \\ \hline
	& 1 & Sow beets. \\ \hline
	& 1 & Start tomatoes. \\ \hline
	& 10 & Sow carrots (wait till soil is at ideal tilling point). \\ \hline
	& 15 & Sow beets. \\ \hline
	& 15 & Sow lettuce. \\ \hline
	& 15 & Buy \& chit potatoes. \\ \hline
	& 15 & Construct tomato trelise. \\ \hline
	& 15 & Construct tomato cloche. \\ \hline
	& 21 & Transplant onions. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{May}} \\ \hline
	& 1 & Sow pole-beans (when soil is warm). \\ \hline
	& 1 & Move tomatoes outside. \\ \hline
	& 1 & Sow broccoli. \\ \hline
	& 1 & Start Winter Squash. \\ \hline
	& 1 & Sow beets. \\ \hline
	& 15 & Sow lettuce. \\ \hline
	& 15 & Plant potatoes. \\ \hline
	& 15 & Sow Summer Squash (before sunny spell). \\ \hline
	& 15 & Transplant Winter Squash (before sunny spell). \\ \hline
	& 21 & Transplat tomatoes. \\ \hline
	& W & Hill potatoes. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{June}} \\ \hline
	& 1 & Sow cucumbers. \\ \hline
	& 1 & Sow kale. \\ \hline
	& 15 & Sow lettuce. \\ \hline
	& 15 & Remove tomato cloche. \\ \hline
	& W & Hill potatoes (until flowering). \\ \hline
	& W & Prune tomatoes. \\ \hline
	& bi-W & Harvest beets. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{July}} \\ \hline
	& 15 & Sow lettuce. \\ \hline
	& 20+ & Harvest cucumber \\ \hline
	& W & Hill potatoes. \\ \hline
	& W & Prune tomatoes. \\ \hline
	& bi-W & Harvest broccoli. \\ \hline
	& bi-W & Harvest beets. \\ \hline
	& bi-W & Harvest pole-beans. \\ \hline
	& bi-W & Harvest tomatoes. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{August}} \\ \hline
	& 1 & Sow short-day onions. \\ \hline
	& 15 & Sow short-day onions. \\ \hline
	& 15 & Sow lettuce. \\ \hline
	& W & Prune tomatoes. \\ \hline
	& bi-W & Harvest broccoli. \\ \hline
	& bi-W & Harvest cucumber. \\ \hline
	& bi-W & Harvest pole-beans. \\ \hline
	& bi-W & Harvest tomatoes. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{September}} \\ \hline
	& 1 & Sow short-day onions. \\ \hline
	& 1 & Sow garlic. \\ \hline
	& 1 & Harvest onions. \\ \hline
	& 1 & Harvest potatoes. \\ \hline
	& 15 & Sow garlic. \\ \hline
	& bi-W & Harvest cucumber. \\ \hline
	& bi-W & Harvest pole-beans. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{October}} \\ \hline
	& 1 & Harvest potatoes. \\ \hline
	& 1 & Sow garlic. \\ \hline
	& 16 & Sow garlic. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{November}} \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{December}} \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{January}} \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	\multicolumn{3}{c}{\textbf{February}} \\ \hline
	& & Thin short-day onions. \\ \hline
	& & Side-dress short-day onions. \\ \hline
	& & Side-dress kale. \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
	& & \\ \hline
\end{longtable}

\end{document}
